---
title: "GreenSlides"
author: "Rotem"
date: "3/13/2023"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Green Slides 1

In this R Markdown document, you will record responses to the questions presented on the green slides from our class. Remember to submit both the (.rmd) file and the generated pdf file after knitting the document. Don't forget to update the "author" and date information accordingly.


### 1 Practicing - Importing Datasets (1)
Import file “table1.txt” to a dataframe (the file is on moodle, under week1 (###1###) ). 
Make sure you:
- skip the first descriptive line
- deal with the “/” quoting the strings
- have columns as strings (and not factors)
- the columns will have names (and not be called V1, V2,..)

```{r q1.1 }
table1<- read.table("table1.txt", header = TRUE, skip =2, quote = "/")
table1

```

#### 1.2) Change the name of the columns to ”gil”,”gova”,”mishkal”, “migdar”
```{r q1.2 }
colnames(table1)<-c('gil', 'gova' , 'mishkal' , 'migdar')
table1

```

### 1.3) Create a column with the names (note that you can name also the rows)
(undoing the argument “row.names="Name",” used when reading the file)
```{r q1.3 }
colnames(table1)<-c('name','gil', 'gova' , 'mishkal' , 'migdar')
table1

```

### 1.4) Display how many rows and columns it has 
```{r q1.4 }
rows_number<- nrow(table1)
cols_number<- ncol(table1)
rows_number
cols_number

```

### 1.5) Drop column “name”
```{r q1.5 }
del_col<-table1[,-1]
 del_col

```


### 2 Practicing - Importing Datasets (2)
Read table2.txt (also in moodle), making sure that:
- all columns  have names (and not be called V1, V2,..)
- all missing values are set to NA
- decimals points are defined with a “.” and not a “,” as in the file
- Sex columns should be of type factor
```{r q2.1 }
 table2<- read.table("table2.txt", header = TRUE, sep = ";", quote = "/", 
                     na.strings = c("--", "**", ""), dec = ",",
                     colClasses = c ("character", "numeric", "numeric", "numeric", "factor"))
 table2

```

### 2.2) Load the Titanic dataset and perform the following: 
(Q1) Display how can we know whether the dataset titanic is a dataframe
(Q2) Convert it to a data frame if it is not
(Q3) Find out how many rows and columns the dataframe has, their names, types, etc.
(Q4) Display the first rows of the dataset
(Q5) show all column names 
(Q6) show the values of a specific column in dataset  (e.g. "Age")
(Q7) What’s the length of the column “Age” ? 
(Q8) What’s the class of the column “Class” ? 
```{r q2.2 }
#Q1
class (Titanic)

#Q2
Titanic<-as.data.frame(Titanic)
class(Titanic)

#Q3
str(Titanic)

#Q4
Titanic[1:4,]

#Q5
colnames(Titanic)

#Q6
Titanic$Age

#Q7
length(Titanic$Age)

#Q8
class(Titanic$Class)

```

### 3 Practicing vectors
3.1) Create a vector of all the letters in the alphabet, in reverse order. 
```{r q3.1 }
rev(letters)

```
3.2) Use the subset() function to create a vector of all the elements of the vector c(1, 2, 3, 4, 5, 6) that are greater than 2:
```{r q3.2}
m_vec<-c(1,2,3,4,5,6)
subset(m_vec,m_vec>2)

```
3.3) Using again the subset() function, create a vector of the first 20 elements of the Fibonacci sequence that are divisible by 3. Note you can use also the fibonacci() function. 
```{r q3.3}
library(numbers)
fibo_vec<-fibonacci(80,TRUE)

 subset(fibo_vec,fibo_vec%%3==0)
```
3.4) Using one line of code, create a vector of the first 100 multiples of 7. Hint: use the seq() function
```{r q3.4}
seq(0,by=7,length.out=100)
```
3.5) Create a vector of the first 20 elements of the sequence of powers of 2 
```{r q3.5}
vec<-0:19
2**vec
```


## Good luck !
